Hemispheric Lateralization and Outcomes After ICH: A Pooled Analysis of Clinical Trials

### 2023-01-18 data-wrangling.qmd
updates

mistie2.combined.demographics <- left_join(mistie2.demographics3, mistie2.demographics)
mistie2.combined.demographics <- left_join(mistie2.demographics2, mistie2.combined.demographics)

@@

@@

VarsTableOne <- c("study","age", "sex", "ethnicity", # Ethnicity
                       "race", # Race
                       "enrolling.country", # Country of Enrolling Site
                       "stroke", 
                       "cad", 
                       "chf", 
                       "afib", 
                       "pvd",
                       "hld",
                       "dm2",
                       "tobacco",
                       "time.to.ed.minutes", # Time from symptom onset to Ed presentation
                       "sbp.initial", # Initial SBP
                       "dbp.initial", # Initial DBP
                       "gcs.baseline", # Baseline GCS
                       "nihss.baseline", # NIHSS
                       "ich.location.baseline", 
                       "ivh",
                      # "hydrocephalus",
                       "ich.volume.cc",
                       "ivh.volume.cc",
                       "phe.volume.cc",
                       "sp.shift.baseline",
                       "mech.ventilation",
                       "intubation.days", 
                       "extubation.date", # Date of extubation
                       "tracheostomy",
                       "trach.date", # Date of Tracheostomy
                       "evd",
                       "evd.days", # Total EVD days
                       "nsgy.evacuation",
                       "nsgy.evacuation.date",  # Date of Evacuation
                       "mrs.30",
                       "mrs.90",
                      "mrs.180",
                      "mrs.365",
                      "euro.mobility.90",
                      "euro.mobility.180",
                      "euro.mobility.365",
                       "euro.selfcare.90",
                      "euro.selfcare.180",
                      "euro.selfcare.365",
                       "euro.usual.90",
                      "euro.usual.180",
                      "euro.usual.365",
                       "euro.pain.90",
                      "euro.pain.180",
                      "euro.pain.365",
                       "euro.anxiety.90",
                      "euro.anxiety.180",
                      "euro.anxiety.365",
                       "euro.vas.90", # EuroQOL VAS
                       "euro.vas.180",
                       "euro.vas.365",
                       "EQ_INDEX.90", # EQ-5D Utility Index,,
                      "current.location.90",
                      "current.location.180",
                      "current.location.365",
                       "ich.laterality",
                  "dnr.binary",
                  "comfort.binary",
                  "dnr.day",
                  "comfort.day"
                  )

@@

# Cleaning up combined dataset
ninds.combined <- ninds.combined %>%
  mutate(sex = case_when(
    sex == "Man" ~ "Male",
    sex == "Male" ~ "Male",
    sex == "Woman" ~ "Female",
    sex == "Female" ~ "Female")) %>%
  mutate(ethnicity = case_when(
    ethnicity == "Hispanic or Latino" ~ "Hispanic or Latino",
    ethnicity == "Not Hispanic or Latino" ~ "Not Hispanic or Latino",
    ethnicity == "Unknown/Not Reported" ~ "NA")) %>%
  mutate(ich.location.baseline = case_when(
    ich.location.baseline == "Basal Ganglia" ~ "Basal Ganglia",
    ich.location.baseline == "Brainstem" ~ "Brainstem",
    ich.location.baseline == "Caudate" ~ "Basal Ganglia",
    ich.location.baseline == "Cerebellum" ~ "Cerebellum",
    ich.location.baseline == "Frontal" ~ "Lobar",
    ich.location.baseline == "Globus Pallidus" ~ "Basal Ganglia",
    ich.location.baseline == "Lobar" ~ "Lobar",
    ich.location.baseline == "Occipital" ~ "Lobar",
    ich.location.baseline == "Other" ~ "Other",
    ich.location.baseline == "Parietal" ~ "Lobar",
    ich.location.baseline == "Primary IVH" ~ "Primary IVH",
    ich.location.baseline == "Probable Primary IVH" ~ "Primary IVH",
    ich.location.baseline == "Putamen" ~ "Basal Ganglia",
    ich.location.baseline == "Temporal" ~ "Lobar",
    ich.location.baseline == "Thalamus" ~ "Thalamus"
  ))

ninds.combined <- ninds.combined %>%
  filter(ich.location.baseline == "Lobar" | 
           ich.location.baseline == "Thalamus" |
           ich.location.baseline == "Basal Ganglia") %>%
  filter(!is.na(ich.laterality))

>>>>

mistie2.combined.demographics <- left_join(mistie2.demographics, mistie2.demographics3)
mistie2.combined.demographics <- left_join(mistie2.combined.demographics, mistie2.demographics2)

@@

mistie2.whole <- mistie2.whole %>%
  mutate(ich.laterality = case_when(
    ich.laterality == "Discrepancy" ~ "NA",
    ich.laterality == "Left" ~ "Left",
    ich.laterality == "Right" ~ "Right",
  ))

@@

VarsTableOne <- c("study","age", "sex", "ethnicity", # Ethnicity
                       "race", # Race
                       "enrolling.country", # Country of Enrolling Site
                       "stroke", 
                       "cad", 
                       "chf", 
                       "afib", 
                       "htn",
                       "hld",
                       "dm2",
                       "tobacco",
                       "time.to.ed.minutes", # Time from symptom onset to Ed presentation
                       "sbp.initial", # Initial SBP
                       "dbp.initial", # Initial DBP
                       "gcs.baseline", # Baseline GCS
                       "nihss.baseline", # NIHSS
                       "ich.location.baseline", 
                       "ivh",
                      # "hydrocephalus",
                       "ich.volume.cc",
                       "ivh.volume.cc",
                       "phe.volume.cc",
                       "sp.shift.baseline",
                       "mech.ventilation",
                       "intubation.days", 
                       "extubation.date", # Date of extubation
                       "tracheostomy",
                       "trach.date", # Date of Tracheostomy
                       "evd",
                       "evd.days", # Total EVD days
                       "nsgy.evacuation",
                       "nsgy.evacuation.date",  # Date of Evacuation
                       "mrs.30",
                       "mrs.90",
                      "mrs.180",
                      "mrs.365",
                      "euro.mobility.90",
                      "euro.mobility.180",
                      "euro.mobility.365",
                       "euro.selfcare.90",
                      "euro.selfcare.180",
                      "euro.selfcare.365",
                       "euro.usual.90",
                      "euro.usual.180",
                      "euro.usual.365",
                       "euro.pain.90",
                      "euro.pain.180",
                      "euro.pain.365",
                       "euro.anxiety.90",
                      "euro.anxiety.180",
                      "euro.anxiety.365",
                       "euro.vas.90", # EuroQOL VAS
                       "euro.vas.180",
                       "euro.vas.365",
                       "EQ_INDEX.90", # EQ-5D Utility Index,,
                      "current.location.90",
                      "current.location.180",
                      "current.location.365",
                       "ich.laterality",
                  "dnr.binary",
                  "comfort.binary",
                  "dnr.day",
                  "comfort.day"
                  )

@@

# Cleaning up combined dataset
ninds.combined <- ninds.combined %>%
  mutate(sex = case_when(
    sex == "Man" ~ "Male",
    sex == "Male" ~ "Male",
    sex == "Woman" ~ "Female",
    sex == "Female" ~ "Female")) %>%
  mutate(ethnicity = case_when(
    ethnicity == "Hispanic or Latino" ~ "Hispanic or Latino",
    ethnicity == "Not Hispanic or Latino" ~ "Not Hispanic or Latino",
    ethnicity == "Unknown/Not Reported" ~ "NA")) 
ninds.combined <- ninds.combined %>%
  filter(ich.location.baseline == "Lobar" | 
           ich.location.baseline == "Thalamus" |
           ich.location.baseline == "Basal Ganglia") %>%
  mutate(ich.laterality = na_if(ich.laterality, "NA")) %>%
  mutate(ethnicity = na_if(ethnicity, "NA")) %>%
  mutate(stroke = na_if(stroke, "NA")) %>%
  mutate(cad = na_if(cad, "NA")) %>%
  mutate(chf = na_if(chf, "NA")) %>%
  mutate(afib = na_if(afib, "NA")) %>%
  mutate(htn = na_if(htn, "NA")) %>%
  mutate(hld = na_if(hld, "NA")) %>%
  mutate(dm2 = na_if(dm2, "NA")) %>%
  mutate(tobacco = na_if(tobacco, "NA")) %>%
  mutate(euro.mobility.90 = na_if(euro.mobility.90, "NA")) %>%
  mutate(euro.selfcare.90 = na_if(euro.selfcare.90, "NA")) %>%
  mutate(euro.usual.90 = na_if(euro.usual.90, "NA")) %>%
  mutate(euro.pain.90 = na_if(euro.pain.90, "NA")) %>%
  mutate(euro.anxiety.90 = na_if(euro.anxiety.90, "NA")) %>%
  mutate(dnr.binary = na_if(dnr.binary, "NA")) %>%
  mutate(comfort.binary = na_if(comfort.binary, "NA")) %>%
  filter(!is.na(ich.laterality))
